\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-26 coqimpl.tex
resolve comments

Family B2 extends B.
  Extend FInductive b : Set 
    := uu : b.
  Extend Family neg_handler.
    Field uu : self_B2.b 
      := self_B2.uu.
  EndFamily. 
EndFamily.
\end{minted}
  \end{minipage}
  \begin{minipage}[t]{0.65\linewidth}
\begin{minted}[fontsize=\footnotesize,escapeinside=@@]{Coq}
  (* Abstraction for Inductive Type *)
Module Type b_3 (self_B: EmptySig_4).
Parameter (b : Set). Parameter (tt ff : b). End b_3.      
Module Type b_6 := b_3 EmptyMod.
  (* Recursor to Set for b *)
Module b_rec_12 (self_B: b_6).
Definition __recursor_type_b_rec :=
  forall P : self_B.b -> Set,
  P self_B.tt -> P self_B.ff 
  -> forall __i : self_B.b, P __i. End b_rec_12. 
  (* Field B.neg_handler.ff *)
Module ff_24 (self_B: b_6) 
             (self_neg_handler@\YZ{'self_neg_handler' instead?}\EDJreply{Yes thx. Though self_neg_handler is not used at all}@: tt_23 self_B).
Definition ff : self_B.b := self_B.tt. End ff_24.
  (* Intermediate Module solely for type checking *)
Module v_33_34 (self_B: neg_handler_26).
Include b_rec_12 self_B.
Parameter (recursor_for_type_checking : __recursor_type_b_rec).
Definition term_for_type_checking :=
  recursor_for_type_checking (fun _ : self_B.b => self_B.b)
    self_B.neg_handler.tt
    self_B.neg_handler.ff.  
End v_33_34.
\end{minted}
  \end{minipage}
\caption{Example Code for Inductive Type}\label{fig:plugin-example2}
\end{figure}

@@

Since the recursor is constructed knowing a concrete inductive type,
thus not inheritable, for all the children, we have to reconstruct and
override with a new recursor (acting like another exhaustiveness
checking in children family\YZ{Why is it 'extra'? Is there already exhaustiveness checking anywhere?}\EDJreply{In the parent family. Maybe extra is a bad wording }). This is affordable since each recursor handler doesn't need
to be rechecked---look at "B2.neg_handler", there is only one new
handler for "uu" and the handlers from the parent
"B.neg_handler.tt,B.neg_handler.ff" have already been type-checked and
inherited (thanks to the fact that they only rely on ``the abstracted
interface'' module "b_3"). Of course, our plugin will ``inherit'' the
recursor "neg" but what the plugin does is doing exhaustiveness
checking, again.\YZ{It'd be good to show *concretely* in Figure 4
(1) code that uses the recursor and how the using code is compiled, (2)
how B2 is compiled and that compiling B2 does not require recompiling
fields inherited from B.}

>>>>

Family B2 extends B.
  Extend FInductive b : Set 
    := uu : b.
  Extend Family neg_handler.
    Field uu : self_B2.b 
      := self_B2.uu.
  EndFamily. 
EndFamily.
\end{minted}
  \end{minipage}
  \begin{minipage}[t]{0.65\linewidth}
\begin{minted}[fontsize=\footnotesize,escapeinside=@@]{Coq}
  (* Abstraction for Inductive Type *)
Module Type b_3 (self_B: EmptySig_4).
Parameter (b : Set). Parameter (tt ff : b). End b_3.      
Module Type b_6 := b_3 EmptyMod.
  (* Recursor to Set for b *)
Module b_rec_12 (self_B: b_6).
Definition __recursor_type_b_rec :=
  forall P : self_B.b -> Set,
  P self_B.tt -> P self_B.ff 
  -> forall __i : self_B.b, P __i. End b_rec_12. 
  (* Field B.neg_handler.ff *)
Module ff_24 (self_B: b_6) 
             (self_neg_handler: tt_23 self_B).
Definition ff : self_B.b := self_B.tt. End ff_24.
  (* Intermediate Module solely for type checking *)
Module v_33_34 (self_B: neg_handler_26).
Include b_rec_12 self_B.
Parameter (recursor_for_type_checking : __recursor_type_b_rec).
Definition term_for_type_checking :=
  recursor_for_type_checking (fun _ : self_B.b => self_B.b)
    self_B.neg_handler.tt
    self_B.neg_handler.ff.  
End v_33_34.
\end{minted}
  \end{minipage}
\caption{Example Code for Inductive Type}\label{fig:plugin-example2}
\end{figure}

@@

Since the recursor is constructed knowing a concrete inductive type,
thus not inheritable, for all the children, we have to reconstruct and
override with a new recursor (therefore serving as exhaustiveness
checking for child families). This is affordable since each recursor handler doesn't need
to be rechecked---look at "B2.neg_handler", there is only one new
handler for "uu" and the handlers from the parent
"B.neg_handler.tt,B.neg_handler.ff" have already been type-checked and
inherited (thanks to the fact that they only rely on ``the abstracted
interface'' module "b_3"). Of course, our plugin will ``inherit'' the
recursor "neg" but what the plugin does is doing exhaustiveness
checking, again.\YZ{It'd be good to show *concretely* in Figure 4
(1) code that uses the recursor and how the using code is compiled, (2)
how B2 is compiled and that compiling B2 does not require recompiling
fields inherited from B.}
